What Happened to The Birth Rate?

### 2022-02-28 outputs/paper/paper.Rmd
figure

## Global Comparison of Fertility Rate Under The Great Recession
It shows that although the United States is at the epicenter of the global economic crisis, it is one of the countries least affected by the financial fallout. Large industrialized nations like the United States, Japan, and Germany have benefited from increasing global demand for relatively stable economies in which to invest. Instead, it is several developing countries, notably those with vulnerable capital accounts and weak macroeconomic fundamentals, that are experiencing severe economic downturns disproportionate to their roles in the crisis[@rank].
\newpage
```{r, least-affected, echo=FALSE, fig.cap="Births per 1000 People of Top Least Affected Countries"}
#Generating time series graphs of births per 1000 people for each least affected country

>>>>

## Global Comparison of Fertility Rate Under The Great Recession
It shows that although the United States is at the epicenter of the global economic crisis, it is one of the countries least affected by the financial fallout. Large industrialized nations like the United States, Japan, and Germany have benefited from increasing global demand for relatively stable economies in which to invest. Instead, it is several developing countries, notably those with vulnerable capital accounts and weak macroeconomic fundamentals, that are experiencing severe economic downturns disproportionate to their roles in the crisis[@rank].

\newpage
```{r least-affected, echo=FALSE, fig.cap="Births per 1000 People of Top Least Affected Countries"}
#Generating time series graphs of births per 1000 people for each least affected country
